The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-06-10 manuscript.Rmd
fix target names

To compare the faunistic lists from the Gulf of Mexico and the Pacific Northwest with records in public databases, we queried the iDigBio and OBIS databases for all records they included in the same geographic boundaries as the lists. After filtering these lists to only include the same higher taxonomic level taxa as the species lists, and keeping only records for which the species could be matched to a species name in WoRMS, we had for the Gulf of Mexico `r nrow(idigbio_gom_records)` and `r nrow(obis_gom_records)` records for iDigBio and OBIS respectively, representing `r dplyr::n_distinct(idigbio_gom_records$worms_valid_name)` and `r dplyr::n_distinct(obis_gom_records$worms_valid_name)` species. For the Pacific Northwest, we retrieved `r nrow(idigbio_kozloff_records)` and `r nrow(obis_kozloff_records)` records for iDigBio and OBIS respectively representing `r dplyr::n_distinct(idigbio_kozloff_records$worms_valid_name)` and `r dplyr::n_distinct(obis_kozloff_records$worms_valid_name)` species. For the Gulf of Mexico, the majority of the species included in the expert lists are recorded in both iDigBio and OBIS (`r format_output(species_in_common$n_spp_gom_idigbio_obis/species_in_common$n_spp_gom*100)` %), or only OBIS (`r format_output(species_in_common$n_spp_gom_obis/species_in_common$n_spp_gom*100)` %) (Fig. \@ref(fig:database-overlap)). For the Pacific Northwest, these proportions were much lower with only `r format_output(species_in_common$n_spp_kozloff_idigbio_obis/species_in_common$n_spp_kozloff*100)`% of the species from the regional list with records in OBIS and iDigBio, and `r format_output(species_in_common$n_spp_kozloff_obis/species_in_common$n_spp_kozloff*100)`%  in OBIS only (Fig. \@ref(fig:database-coverage)).

>>>>

To compare the faunistic lists from the Gulf of Mexico and the Pacific Northwest with records in public databases, we queried the iDigBio and OBIS databases for all records they included in the same geographic boundaries as the lists. After filtering these lists to only include the same higher taxonomic level taxa as the species lists, and keeping only records for which the species could be matched to a species name in WoRMS, we had for the Gulf of Mexico `r nrow(idigbio_gom_records)` and `r nrow(obis_gom_records)` records for iDigBio and OBIS respectively, representing `r dplyr::n_distinct(idigbio_gom_records$worms_valid_name)` and `r dplyr::n_distinct(obis_gom_records$worms_valid_name)` species. For the Pacific Northwest, we retrieved `r nrow(idigbio_pnw_records)` and `r nrow(obis_kozloff_records)` records for iDigBio and OBIS respectively representing `r dplyr::n_distinct(idigbio_pnw_records$worms_valid_name)` and `r dplyr::n_distinct(obis_kozloff_records$worms_valid_name)` species. For the Gulf of Mexico, the majority of the species included in the expert lists are recorded in both iDigBio and OBIS (`r format_output(species_in_common$n_spp_gom_idigbio_obis/species_in_common$n_spp_gom*100)` %), or only OBIS (`r format_output(species_in_common$n_spp_gom_obis/species_in_common$n_spp_gom*100)` %) (Fig. \@ref(fig:database-overlap)). For the Pacific Northwest, these proportions were much lower with only `r format_output(species_in_common$n_spp_kozloff_idigbio_obis/species_in_common$n_spp_kozloff*100)`% of the species from the regional list with records in OBIS and iDigBio, and `r format_output(species_in_common$n_spp_kozloff_obis/species_in_common$n_spp_kozloff*100)`%  in OBIS only (Fig. \@ref(fig:database-coverage)).
